Unknown

### 2024-04-05 ms/ms.qmd
drafted methods for regression of light habitat on aa

We tested for effects of light intensity, light treatment, accession, and their interactions on \aax. All models included effects of light intensity and light treatment, as well as random effects of accession and replicate within accession. More complex models included interactions between light intensity and light treatment, as well as random effects of accession on the effects of light intensity and light treatment. We used a weakly informative normal prior with mean $0$ and standard deviation $10$ for fixed effects light intensity and treatment. We used a weakly informative normal prior with mean $-5$ and standard deviation $5$ for the the random effect standard deviation of replicate within accession. We accounted for the phylogenetic structure among the random effects of accession using an Ornstein-Uhlenbeck (OU) process [@hansen_stabilizing_1997]. We used a weakly informative normal prior with mean $0$ and standard deviation $10$ on OU parameters. We modeled the residual standard deviation on a log-link scale with effects of light intensity and light treatment. We used a weakly informative normal prior with mean $-3$ and standard deviation $5$ on the residual standard deviation intercept and a weakly informative normal prior with mean $0$ and standard deviation $1$ on the effects of light intensity and light treatment on the residual standard deviation.

WORKING HERE - TABLE OR SOMETHING SUMMARIZING MODELS?

>>>>

We tested for effects of light intensity, light treatment, accession, and their interactions on \aax. All models included effects of light intensity and light treatment, as well as random effects of accession and replicate within accession. More complex models included interactions between light intensity and light treatment, as well as random effects of accession on the effects of light intensity and light treatment. We used a weakly informative normal prior with mean $0$ and standard deviation $10$ for fixed effects light intensity and treatment. We used a weakly informative normal prior with mean $-3$ and standard deviation $5$ for the the random effect standard deviation of replicate within accession. We accounted for the phylogenetic structure among the random effects of accession using an Ornstein-Uhlenbeck (OU) process [@hansen_stabilizing_1997]. We used a weakly informative normal prior with mean $0$ and standard deviation $10$ on OU parameters. We modeled the residual standard deviation on a log-link scale with effects of light intensity and light treatment. We used a weakly informative normal prior with mean $-3$ and standard deviation $5$ on the residual standard deviation intercept and a weakly informative normal prior with mean $0$ and standard deviation $1$ on the effects of light intensity and light treatment on the residual standard deviation.

##### Effects of native light habitat on accession-level \aax

We tested a linear effect of native light habitat on accession-level \aax. In Models 1 and 2, we used the random intercept of \aax{} as a response variable; in model 3 we used the random intercept plus the random effect of accession at high light intensity; in model 4 we used the random intercept plus the random effect of accession in the sun treatment; in model 5 we used the random intercept plus the random effects of accession at high light intensity and sun treatment. We used a weakly informative normal prior with mean $0$ and standard deviation $1$ for the slope and intercept. We accounted for the phylogenetic structure among the model residuals using an (OU) process. We used a weakly informative normal prior with mean $0$ and standard deviation $10$ on OU parameters.

WORKING HERE - TABLE OR SOMETHING SUMMARIZING MODELS?
- TABLE SUMMARIZING PARAMETERS
